### 2022-04-19 outputs/paper/paper.Rmd
Data preparation and gg plot (started)

---
title: "Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Last sentence."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(dplyr)
library(knitr)
library(scales)
```

# Introduction
First paragraph

Second paragraph

Third paragraph

This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.

# Data
```{r, include=FALSE, echo=FALSE}
# Read the reduced and cleaned data, modification done in data-preparation.r file
reduced_data1 <- read_csv("outputs/data/prepared_gss1.csv")
reduced_data2 <- read_csv("outputs/data/prepared_gss2.csv")
c_data <- read_csv("outputs/data/combined_data.csv")
```

Data Explanation

```{r fig1,echo=FALSE,fig.cap = "Distribution of national spending on foreign aid"}
c_data$nataid <- factor(c_data$nataid,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(nataid)  %>%
   ggplot(aes(x= nataid,group=name)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
    facet_grid(~name) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on foreign aid"}
c_data$nataid <- factor(c_data$nataid,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(nataid)  %>%
   ggplot(aes(x= nataid,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = "National Spending Levels by Year") +
    facet_grid(~year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

\newpage

# Results

# Discussion

## Summary

## Weaknesses and how we should proceed in the future

\newpage

\appendix

# Appendix {-}

## End Page

Thank you for participating in our survey. If you have any questions please do not hesitate to contact us.
sangwoong.lee@maill.utoronto.ca and young.suk@mail.utoronto.ca

\newpage

# References
Smith, Tom W., Davern, Michael, Freese, Jeremy, and Morgan, Stephen L., General Social Surveys, 1972-2018 [machine-readable data file] /Principal Investigator, Smith, Tom W.; Co-Principal Investigators, Michael Davern, Jeremy Freese and Stephen L. Morgan; Sponsored by National Science Foundation. --NORC ed.-- Chicago: NORC, 2019.

U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.

### 2022-04-19 scripts/data-preparation.R

@@ -42,27 +42,7 @@ reduced_data1 <-
          natroad,
          natsci,
          natsoc,
-         eqwlth,
-         ) %>%
-  rename(nataid2018 = nataid,
-         natarms2018 = natarms,
-         natchld2018 = natchld,
-         natcity2018 = natcity,
-         natcrime2018 = natcrime,
-         natdrug2018 = natdrug,
-         nateduc2018 = nateduc,
-         natenrgy2018 = natenrgy,
-         natenvir2018 = natenvir,
-         natfare2018 = natfare,
-         natheal2018 = natheal,
-         natmass2018 = natmass,
-         natpark2018 = natpark,
-         natrace2018 = natrace,
-         natroad2018 = natroad,
-         natsci2018 = natsci,
-         natsoc2018 = natsoc,
-         eqwlth2018 = eqwlth
-  )
+         eqwlth)
 reduced_data2 <-
   raw_data2 %>% 
   select(nataid,
@@ -82,8 +62,32 @@ reduced_data2 <-
          natroad,
          natsci,
          natsoc,
-         eqwlth,
-  )%>%
+         eqwlth)
+reduced_data1$year <- "2018"
+reduced_data2$year <- "2021"
+c_data <- rbind(reduced_data1, reduced_data2)
+reduced_data1  <- 
+  reduced_data1  %>% 
+  rename(nataid2018 = nataid,
+         natarms2018 = natarms,
+         natchld2018 = natchld,
+         natcity2018 = natcity,
+         natcrime2018 = natcrime,
+         natdrug2018 = natdrug,
+         nateduc2018 = nateduc,
+         natenrgy2018 = natenrgy,
+         natenvir2018 = natenvir,
+         natfare2018 = natfare,
+         natheal2018 = natheal,
+         natmass2018 = natmass,
+         natpark2018 = natpark,
+         natrace2018 = natrace,
+         natroad2018 = natroad,
+         natsci2018 = natsci,
+         natsoc2018 = natsoc,
+         eqwlth2018 = eqwlth)
+reduced_data2  <-
+  reduced_data2  %>% 
   rename(nataid2021 = nataid,
[…]

### 2022-04-19 outputs/paper/paper.Rmd
test

@@
 
-```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on foreign aid"}
+```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on "}
 c_data$nataid <- factor(c_data$nataid,                                  

### 2022-04-20 outputs/paper/paper.Rmd
Data preparation and gg plot edited (1st)

@@
   drop_na(nataid)  %>%
-   ggplot(aes(x= nataid,group=name)) + 
+   ggplot(aes(x= nataid,group=year)) + 
     geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
@@
     labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
-    facet_grid(~name) +
+    facet_grid(~year) +
     scale_y_continuous(labels = scales::percent) +
@@
 
-```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on "}
-c_data$nataid <- factor(c_data$nataid,                                  
+```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on arms"}
+c_data$natarms <- factor(c_data$natarms,                                  
                   levels = c("Too little", "About right", "Too much"))
 c_data  %>%
-  drop_na(nataid)  %>%
-   ggplot(aes(x= nataid,group=year)) + 
+  drop_na(natarms)  %>%
+   ggplot(aes(x= natarms,group=year)) + 
     geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
@@
                    y= ..prop.. ), stat= "count", vjust = -0.4) +
-    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = "National Spending Levels by Year") +
-    facet_grid(~year) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
+    facet_grid(~ year) +
     scale_y_continuous(labels = scales::percent) +
@@
                                  values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig3,echo=FALSE,fig.cap = "Distribution of national spending on childcare"}
+c_data$natchld <- factor(c_data$natchld,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natchld)  %>%
+   ggplot(aes(x= natchld,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r}
+
 ```

### 2022-04-20 scripts/data-preparation.R

@@ -66,293 +66,109 @@ reduced_data2 <-
 reduced_data1$year <- "2018"
 reduced_data2$year <- "2021"
 c_data <- rbind(reduced_data1, reduced_data2)
-reduced_data1  <- 
-  reduced_data1  %>% 
-  rename(nataid2018 = nataid,
-         natarms2018 = natarms,
-         natchld2018 = natchld,
-         natcity2018 = natcity,
-         natcrime2018 = natcrime,
-         natdrug2018 = natdrug,
-         nateduc2018 = nateduc,
-         natenrgy2018 = natenrgy,
-         natenvir2018 = natenvir,
-         natfare2018 = natfare,
-         natheal2018 = natheal,
-         natmass2018 = natmass,
-         natpark2018 = natpark,
-         natrace2018 = natrace,
-         natroad2018 = natroad,
-         natsci2018 = natsci,
-         natsoc2018 = natsoc,
-         eqwlth2018 = eqwlth)
-reduced_data2  <-
-  reduced_data2  %>% 
-  rename(nataid2021 = nataid,
-         natarms2021 = natarms,
-         natchld2021 = natchld,
-         natcity2021 = natcity,
-         natcrime2021 = natcrime,
-         natdrug2021 = natdrug,
-         nateduc2021 = nateduc,
-         natenrgy2021 = natenrgy,
-         natenvir2021 = natenvir,
-         natfare2021 = natfare,
-         natheal2021 = natheal,
-         natmass2021 = natmass,
-         natpark2021 = natpark,
-         natrace2021 = natrace,
-         natroad2021 = natroad,
-         natsci2021 = natsci,
-         natsoc2021 = natsoc,
-         eqwlth2021 = eqwlth)
 # Modify scales name for simplicity
-reduced_data1 <- 
-  reduced_data1 %>% 
-  mutate(nataid2018 = case_when(
-    nataid2018 == 1 ~ "Too little",
-    nataid2018 == 2 ~ "About right",
-    nataid2018 == 3 ~ "Too much",
-  ))
-reduced_data2 <- 
-  reduced_data2 %>% 
-  mutate(nataid2021 = case_when(
[…]

### 2022-04-20 scripts/data-preparation.R
Variables added

@@ -42,7 +42,11 @@ reduced_data1 <-
          natroad,
          natsci,
          natsoc,
-         eqwlth)
+         eqwlth,
+         health,
+         helpsick,
+         helpnot,
+         helppoor)
 reduced_data2 <-
   raw_data2 %>% 
   select(nataid,
@@ -62,7 +66,11 @@ reduced_data2 <-
          natroad,
          natsci,
          natsoc,
-         eqwlth)
+         eqwlth,
+         health,
+         helpsick,
+         helpnot,
+         helppoor)
 reduced_data1$year <- "2018"
 reduced_data2$year <- "2021"
 c_data <- rbind(reduced_data1, reduced_data2)
@@ -169,6 +177,36 @@ c_data <-
     natsoc == 1 ~ "Too little",
     natsoc == 2 ~ "About right",
     natsoc == 3 ~ "Too much"))
+c_data <-
+  c_data  %>% 
+  mutate(health = case_when(
+    health == 1 ~ "Excellent",
+    health == 2 ~ "Good",
+    health == 3 ~ "Fair",
+    health == 4 ~ "Poor"))
+c_data <-
+  c_data  %>% 
+  mutate(helpsick = case_when(
+    helpsick == 1 ~ "Yes",
+    helpsick == 2 ~ "Somewhat",
+    helpsick == 3 ~ "Both",
+    helpsick == 5 ~ "No"))
+c_data <-
+  c_data  %>% 
+  mutate(helpnot = case_when(
+    helpnot == 1 ~ "Yes",
+    helpnot == 2 ~ "Somewhat",
+    helpnot == 3 ~ "Both",
+    helpnot == 5 ~ "No"))
+c_data <-
+  c_data  %>% 
+  mutate(helppoor = case_when(
+    helppoor == 1 ~ "Yes",
+    helppoor == 2 ~ "Somewhat",
+    helppoor == 3 ~ "Both",
+    helppoor == 5 ~ "No"))
+
+
 #### Save ####
 write_csv(reduced_data1, "outputs/data/prepared_gss1.csv")
 write_csv(reduced_data2, "outputs/data/prepared_gss2.csv")

### 2022-04-20 outputs/paper/paper.Rmd
Data preparation and gg plot edited (2nd)

@@
                    y= ..prop.. ), stat= "count", vjust = -0.4) +
-    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
+           "National Spending on Foreign Aid") +
     facet_grid(~year) +
@@
                    y= ..prop.. ), stat= "count", vjust = -0.4) +
-    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
+           "National Spending on Arms") +
     facet_grid(~ year) +
@@
                    y= ..prop.. ), stat= "count", vjust = -0.4) +
-    labs(x = element_blank(),y = "Percent", fill = "National Spending Level") +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
+           "National Spending on Childcare") +
     facet_grid(~ year) +
@@
 
-```{r}
+```{r fig4,echo=FALSE,fig.cap = "Distribution of national spending on big cities problems"}
+c_data$natcity <- factor(c_data$natcity,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natcity)  %>%
+   ggplot(aes(x= natcity,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
+           "National Spending on Big Cities Problems") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
 
+```{r fig5,echo=FALSE,fig.cap = "Distribution of national spending on halting crime rates"}
+c_data$natcrime <- factor(c_data$natcrime,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natcrime)  %>%
+   ggplot(aes(x= natcrime,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title =
+           "National Spending on Halting Crime Rates") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig6,echo=FALSE,fig.cap = "Distribution of national spending on dealing with drug addicts"}
+c_data$natdrug <- factor(c_data$natdrug,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natdrug)  %>%
+   ggplot(aes(x= natdrug,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Dealing with Drug Addicts") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig7,echo=FALSE,fig.cap = "Distribution of national spending on improving education"}
+c_data$nateduc <- factor(c_data$nateduc,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(nateduc)  %>%
+   ggplot(aes(x= nateduc,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Improving Education") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig8,echo=FALSE,fig.cap = "Distribution of national spending on developing alternatives energy sources"}
+c_data$natenrgy <- factor(c_data$natenrgy,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natenrgy)  %>%
+   ggplot(aes(x= natenrgy,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Developing Alternatives Energy") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig9,echo=FALSE,fig.cap = "Distribution of national spending on protecting environment"}
+c_data$natenvir <- factor(c_data$natenvir,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natenvir)  %>%
+   ggplot(aes(x= natenvir,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Protecting Environment") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig10,echo=FALSE,fig.cap = "Distribution of national spending on Welfare"}
+c_data$natfare <- factor(c_data$natfare,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natfare)  %>%
+   ggplot(aes(x= natfare,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Welfare") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig11,echo=FALSE,fig.cap = "Distribution of national spending on improving health"}
+c_data$natheal <- factor(c_data$natheal,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natheal)  %>%
+   ggplot(aes(x= natheal,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Improving Health") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig12,echo=FALSE,fig.cap = "Distribution of national spending on mass transportation"}
+c_data$natmass <- factor(c_data$natmass,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natmass)  %>%
+   ggplot(aes(x= natmass,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Mass Transportation") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig13,echo=FALSE,fig.cap = "Distribution of national spending on park and recreation"}
+c_data$natpark <- factor(c_data$natpark,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natpark)  %>%
+   ggplot(aes(x= natpark,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Park and Recreation") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig14,echo=FALSE,fig.cap = "Distribution of national spending on improving the conditions of black"}
+c_data$natrace <- factor(c_data$natrace,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natrace)  %>%
+   ggplot(aes(x= natrace,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Improving Conditions of Black") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig15,echo=FALSE,fig.cap = "Distribution of national spending on highway and bridges"}
+c_data$natroad <- factor(c_data$natroad,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natroad)  %>%
+   ggplot(aes(x= natroad,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Highway and Bridge") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig16,echo=FALSE,fig.cap = "Distribution of national spending on scientific research"}
+c_data$natsci <- factor(c_data$natsci,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natsci)  %>%
+   ggplot(aes(x= natsci,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Supporting Scientific Research") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig17,echo=FALSE,fig.cap = "Distribution of national spending on social security"}
+c_data$natsoc <- factor(c_data$natsoc,                                  
+                  levels = c("Too little", "About right", "Too much"))
+c_data  %>%
+  drop_na(natsoc)  %>%
+   ggplot(aes(x= natsoc,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = 
+           "National Spending on Seocial Security") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
+```
+
+```{r fig18,echo=FALSE,fig.cap = "Respondents self Health Conditions"}
+c_data$health <- factor(c_data$health,                                  
+                  levels = c("Poor", "Fair", "Good", "Excellent"))
+c_data  %>%
+  drop_na(health)  %>%
+   ggplot(aes(x= health,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "Health Conditions", title = 
+           "Respondents' Health Conditions by Self Assessment") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Poor", "2" = "Fair", "3" = "Good", "4" = "Excellent"),
+                                 values=c("#F0E442", "#0072B2", "#D55E00", "#CC79A7"))
+```
+
+```{r fig19,echo=FALSE,fig.cap = "Government and Individuals on Health"}
+c_data$helpsick <- factor(c_data$helpsick,                                  
+                  levels = c("No", "Somewhat", "Both", "Yes"))
+c_data  %>%
+  drop_na(helpsick)  %>%
+   ggplot(aes(x= helpsick,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "Response", title = 
+           "Should Government Be Responsible for Taking Care of Individuals?") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "No", "2" = "Somewhat", "3" = "Both", "4" = "Yes"),
+                                 values=c("#F0E442", "#0072B2", "#D55E00", "#CC79A7"))
+```
+
+```{r fig20,echo=FALSE,fig.cap = "Government and Individuals on Poor"}
+c_data$helppoor <- factor(c_data$helppoor,                                  
+                  levels = c("No", "Somewhat", "Both", "Yes"))
+c_data  %>%
+  drop_na(helppoor)  %>%
+   ggplot(aes(x= helppoor,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4) +
+    labs(x = element_blank(),y = "Percent", fill = "Response", title = 
+           "Should Government Be Responsible for Improving Standard Livings?") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "No", "2" = "Somewhat", "3" = "Both", "4" = "Yes"),
+                                 values=c("#F0E442", "#0072B2", "#D55E00", "#CC79A7"))
+
+```
+
+```{r fig21,echo=FALSE,fig.cap = "Government Reducing Income Differences"}
+c_data$eqwlth <- factor(c_data$eqwlth)
+
+c_data  %>%
+  drop_na(eqwlth)  %>%
+   ggplot(aes(x= eqwlth,group=year)) + 
+    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
+    geom_text(aes( label = scales::percent(..prop..),
+                   y= ..prop.. ), stat= "count", vjust = -0.4, size = 3) +
+    labs(x = element_blank(),y = "Percent", fill = "Levels", title = 
+           "Should Government Be Responsible for Reducing Income Differences") +
+    facet_grid(~ year) +
+    scale_y_continuous(labels = scales::percent) +
+    scale_fill_manual(labels = c("1" = "Yes", "7" = "No"),
+                                 values=c("#01378C","#2cd18c", "#ff3d3d","#F0E442", "#0072B2", "#D55E00", "#CC79A7"))
 ```

### 2022-04-20 scripts/data-preparation.R

@@ -45,7 +45,6 @@ reduced_data1 <-
          eqwlth,
          health,
          helpsick,
-         helpnot,
          helppoor)
 reduced_data2 <-
   raw_data2 %>% 
@@ -69,7 +68,6 @@ reduced_data2 <-
          eqwlth,
          health,
          helpsick,
-         helpnot,
          helppoor)
 reduced_data1$year <- "2018"
 reduced_data2$year <- "2021"
@@ -193,19 +191,11 @@ c_data <-
     helpsick == 5 ~ "No"))
 c_data <-
   c_data  %>% 
-  mutate(helpnot = case_when(
-    helpnot == 1 ~ "Yes",
-    helpnot == 2 ~ "Somewhat",
-    helpnot == 3 ~ "Both",
-    helpnot == 5 ~ "No"))
-c_data <-
-  c_data  %>% 
   mutate(helppoor = case_when(
     helppoor == 1 ~ "Yes",
     helppoor == 2 ~ "Somewhat",
     helppoor == 3 ~ "Both",
     helppoor == 5 ~ "No"))
-
 
 #### Save ####
 write_csv(reduced_data1, "outputs/data/prepared_gss1.csv")

### 2022-04-22 scripts/00-simulation.R
Add files via upload
simulation filed added

@@ -1,0 +1,146 @@
+### Preamble ###
+# Purpose: Obtain and prepare data about children 12 to 59 months of age according to immunization 
+# status and method of reporting immunization status, by selected background characteristics. 
+# Author: SangWoong Lee and Young Suk
+# Email: sangwoong.lee@mail.utoronto.ca and young.suk@mail.utoronto.ca
+# Date 24 March 2022
+# prerequisites: - 
+
+### Worksapce set-up ###
+library(janitor)
+library(lubridate)
+library(tidyverse)
+
+set.seed(777)
+sample_size <- 3000
+simulated_urban_rural <- 
+  tibble(
+    variables = 
+      c(
+        rep('Urban',1),
+        rep('Rural',1)
+      ),
+    Health_record = 
+      runif(n=2,
+            min = 0,
+            max = 100),
+    Mother_record = 
+      runif(n= 2,
+            min = 0,
+            max = 100 -Health_record),
+    immunization = Mother_record + Health_record,
+    non_immunization = 100 - immunization,
+    number_of_childeren = 
+      as.numeric(rmultinom(n = 1, size = 3000, prob = rep(1/2, 2)))
+  )
+simulated_region <- 
+  tibble(
+    variables = 
+      c(
+        rep('North',1),
+        rep('Northeast',1),
+        rep('Central',1),
+        rep('South',1),
+        rep('Bangkok',1)
+      ),
+    Health_record = 
+      runif(n=5,
+            min = 0,
+            max = 100),
+    Mother_record = 
+      runif(n= 5,
+            min = 0,
+            max = 100 -Health_record),
+    immunization = Mother_record + Health_record,
+    non_immunization = 100 - immunization,
+    number_of_childeren = 
+      as.numeric(rmultinom(n = 1, size = 3000, prob = rep(1/5, 5)))
+  )
+simulated_education <- 
+  tibble(
+    variables = 
+      c(
+        rep('No_education',1),
+        rep('Primary',1),
+        rep('Secondary',1),
+        rep('Higher',1)
+      ),
+    Health_record = 
+      runif(n=4,
+            min = 0,
+            max = 100),
+    Mother_record = 
+      runif(n= 4,
+            min = 0,
+            max = 100 -Health_record),
+    immunization = Mother_record + Health_record,
+    non_immunization = 100 - immunization,
+    number_of_childeren = 
[…]

### 2022-04-22 scripts/00-simulation.R
Simulation updated

@@ -1,9 +1,8 @@
 ### Preamble ###
-# Purpose: Obtain and prepare data about children 12 to 59 months of age according to immunization 
-# status and method of reporting immunization status, by selected background characteristics. 
-# Author: SangWoong Lee and Young Suk
-# Email: sangwoong.lee@mail.utoronto.ca and young.suk@mail.utoronto.ca
-# Date 24 March 2022
+# Purpose: Obtain and prepare data about U.S citizens opinions on Government spending 
+# Author: SangWoong Lee 
+# Email: sangwoong.lee@mail.utoronto.ca
+# Date 22 April 2022
 # prerequisites: - 
 
 ### Worksapce set-up ###
@@ -13,134 +12,157 @@ library(tidyverse)
 
 set.seed(777)
 sample_size <- 3000
-simulated_urban_rural <- 
+simulate_national_spending <- 
   tibble(
-    variables = 
-      c(
-        rep('Urban',1),
-        rep('Rural',1)
-      ),
-    Health_record = 
-      runif(n=2,
-            min = 0,
-            max = 100),
-    Mother_record = 
-      runif(n= 2,
-            min = 0,
-            max = 100 -Health_record),
-    immunization = Mother_record + Health_record,
-    non_immunization = 100 - immunization,
-    number_of_childeren = 
-      as.numeric(rmultinom(n = 1, size = 3000, prob = rep(1/2, 2)))
+    natarms = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natchld = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natcity = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natcrime = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natdrug = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    nateduc = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natenrgy = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natenvir = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natfare = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natheal = 
+      round(runif(n=3000,
+                  min = 1,
+                  max = 3)),
+    natmass = 
+      round(runif(n=3000,
[…]

### 2022-04-22 scripts/data-preparation.R
unncessary data deleted

@@ -198,9 +198,7 @@ c_data <-
     helppoor == 5 ~ "No"))
 
 #### Save ####
-write_csv(reduced_data1, "outputs/data/prepared_gss1.csv")
-write_csv(reduced_data2, "outputs/data/prepared_gss2.csv")
-write_csv(c_data, "outputs/data/combined_data.csv")
+write_csv(c_data, 'outputs/combined_data.csv')
 
 
          

### 2022-04-22 outputs/paper/paper.Rmd
title updated

@@
 ---
-title: "Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
-subtitle: "Possible factors effecting 2016 election"
+title: "Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
+subtitle: "COVID-19 influences on U.S citizens' mind regarding government actions"
 author: 
@@
 # Read the reduced and cleaned data, modification done in data-preparation.r file
-reduced_data1 <- read_csv("outputs/data/prepared_gss1.csv")
-reduced_data2 <- read_csv("outputs/data/prepared_gss2.csv")
-c_data <- read_csv("outputs/data/combined_data.csv")
+c_data <- read_csv("outputs/combined_data.csv")
 ```

### 2022-04-22 outputs/paper/paper.Rmd
Data session writing (1)

@@
 library(scales)
+library(modelsummary)
 ```
@@
 # Introduction
-First paragraph
+First paragraph : broader context for motivation
 
-Second paragraph
+Second paragraph : some detail about what the paper is about
 
-Third paragraph
+Third paragraph: a clear gap that needs to be filled
+
+Fourth: what was done, what was found
+
+5: why it is important
 
@@
 Data Explanation
+
+For this paper, my aim is to find out changes in U.S citizens' minds regarding government before and after COVID-19 outbreak.
+Following that, I obtained datasets from U.S GSS 2018 and 2021 since COVID-19 was first reported on 2019.
+There are numerous surveys about COVID-19, however in order to analyze changes in general thoughts, they are not as appropriate as U.S GSS.
+Most COVID-19 surveys were specifically aimed for health care fields.
+For instance, whether healthcare system was enough to cover all patients or not was a major point for most COVID-19 surveys.
+On the other hand, U.S GSS datasets included more various fields such as national spending on drug, crime and etc, thus it can rather represent more general changes.
+Among countless variables existing in U.S GSS, I chose opinions on national spending and government actions.
+Since I used two different years for comparison, I had to find out which variables were in common, then combined them.
+
+The variables I collected were as followed:
+1) National spending on various fields (foreign aids, arms, children, big cities, crime, drug,
+education, new energy, environment, fare, healthcare, mass transportation, parks, race, roads, science and social security )
+
+2) Government's actions (income equality, the sick, the poor)
+
+3) Respondents' health
+
+There exists 17 variables in national spending and 3 variables regarding government actions.
+Since, dealing with all variables in this session would take much spaces, for those that did not change much between 2018 and 2022, I am going to deal with in Appendix.
 

### 2022-04-22 outputs/paper/paper.Rmd
Data session writing (2)

--- 2022-04-22 outputs/paper/paper.Rmd
@@
 
-Data Explanation
+For this paper, I aimed to find out changes in U.S citizens' minds regarding the government before and after COVID-19 outbreak.
+Following that, I obtained datasets from U.S GSS 2018 and 2021 considering first outbreak of COVID-19, which was in Dec 2019.
+There are numerous surveys about COVID-19, however in order to observe general thought changes, they are not as appropriate as U.S GSS.
+Most COVID-19 surveys were specifically aimed for healthcare fields.
+For instance, whether healthcare system was enough to cover all patients or not was a major point for most COVID-19 surveys.
+On the other hand, U.S GSS datasets included more various fields such as national spending on drug, crime and etc, thus it can rather represent more general changes than specific areas.
+Among countless variables existing in U.S GSS, I chose national spending levels and government actions.
+Since I needed to use two different years for comparison, I had to extract variables that were in common, then combined them.
+Also, since number of samples was different, converting sample size to percentage was needed.
+
+The variables I collected were as followed:
+
+1) National spending on various fields (foreign aids, arms, children, big cities, crime, drug,
+education, new energy, environment, fare, healthcare, mass transportation, parks, race, roads, science and social security )
+
+2) Government's actions (income equality, the sick, the poor)
+
+3) Respondents' health
+
+There exists 17 variables in national spending and 3 variables regarding government actions.
+Since, dealing with all variables in this session would take much spaces, for those that did not change much from 2018 to 2022, I am going to deal with in Appendix.
+
+First, to make the demarcation between data session and appendix, I focused on two parts: whether there existed different patterns or noticeable changes between two graphs 2018 and 2021.
+For instance, figure \@ref(fig:fig7) shows us same pattern between 2018 and 2022, and there exists subtle changes.
+On the other hand, although figure \@ref(fig:fig6) presents the same pattern, changes in percentage are relatively fluctuating than others.
+For an another example, figure \@ref(fig:fig2) presents different pattern between 2018 and 2021.
+Therefore, with respect to two the aspects, I am going to explain my data here.
+
+1) National spending (Foreign aid, Arms, Drug addicts, Welfare, race)
+
+- Foreign Aid
+
+Let's take a look at figure \@ref(fig:fig1).
+In general, majority of respondents answered either "Too much" or "About right".
+What is interesting here is 7.8% decrease in "Too little" and 9.2% increase in "Too much".
+These numbers might seem subtle, however if we put this into whole population of U.S, it is 25.7 million and 30.34 million respectively.
+
+- Arms
+
+If you take a look at figure \@ref(fig:fig2), you can observe two different patterns.
+"Too little" and "Too much" in 2018 has been reversed in 2021.
+If you think about U.S withdraw from Afghanistan in 2021, this would make sense.
+
+- Drug Addicts
+
+This is an indicator that contradicts with drug overdose death data.
+According to CDC, death rate from drug overdoes is increasing over years.
+However, figure \@ref(fig:fig6) presents the decreasing in "Too little", although it is  the highest among three indicators.
+
+- Welfare
+
+Welfare graph seems relatively obvious than those above.
+Figure \@ref(fig:fig10) shows us that more voices on increasing national spending on welfare.
+Here I strongly suspect the COVID-19 outbreak as a main reason for the change.
+
+- Race
+
+Figure \@ref(fig:fig14) shows the national spending on improvement in Black conditions.
+Even though "Too little" is higher than others, it decreased over the years.
+On the other hand, "Too much" increased by 9.4%.
+As I mentioned above, this percent is huge.
+Unfortunately, there is a limit in this variable.
+Black alone cannot represent all races in U.S, thus it is hard to generalize all races from this data.
+However, the differences observed in this graph possesses valuable meanings.
+
+2) Government actions
+
+- Income equality and help poor
+
+This two variables are very similar.
+Income equality is regarding whether government should impose more taxes on the rich for better income equality or not, and help poor is whether government should be responsible for helping the poor or not.
+Thankfully, they both present similar pattern, which enhances the reliability about the survey.
+Majority thinks that government and individuals both are responsible for income differences.
+One thing to notice here is that voice for government responsibility increased over years.
+
+- The sick
+
+The two graph in figure \@ref(fig:fig19) seems very similar, but this does not mean that it does not possess valuable meanings.
+In 2020 - 2021 when U.S GSS 2021 was conducted, although COVID-19 cases did not surge up as much as 2022, but with eyes in 2021, it was increasing.
+However, before and after COVID-19, there is no difference in response regarding government actions toward the sick.
+Majority think that more actions needed toward the sick from the government
+
+3) Respondents' health
+
+Most of participants were in good health conditions in figure \@ref(fig:fig18). One thing to notice here is that participants health conditions increased.
 
@@
 # Results
+According to Forbes research, foreign aid spent by U.S is decreasing over years which was 46 billion dollars in 2018 and 38 billion dollars in 2021.
+In other words, this contradiction means that there could be another factors that possibly influenced thoughts on foreign aids.
 
@@
 --NORC ed.-- Chicago: NORC, 2019.
+https://www.forbes.com/sites/adamandrzejewski/2021/08/04/new-report-nearly-300-billion-in-foreign-aid-spent-by-us-government/?sh=6e3454774374
+https://www.cdc.gov/drugoverdose/deaths/index.html
 

### 2022-04-22 outputs/paper/paper.Rmd
Data session writing (3)

@@
 # Appendix {-}
+In this session, I am going to deal with remained data explanation. Since no dramatic changes were observed in remained variables, I combined them by patterns.
+
+1) Decrease in "Too little" and increase in "About right" and "Too much"
+
+- Big cities Problems (figure \@ref(fig:fig4))
+- Education (figure \@ref(fig:fig7))
+
+2) Decrease in "Too little" and "About right" and increase in "Too much"
+
+- Childcare (figure \@ref(fig:fig3))
+- Crime rates (figure \@ref(fig:fig5))
+- New energy (figure \@ref(fig:fig8))
+- Social security (figure \@ref(fig:fig17))
+
+3) Decrease in "About right" and increase in "Too little" and "Too much"
+
+- Environment (figure \@ref(fig:fig9))
+
+4) Decrease in "Too much" and increase in "Too little and "About right"
+
+- Road (figure \@ref(fig:fig15))
+
+4) only subtle changes.
+
+- Mass transportation (figure \@ref(fig:fig12))
+- Park and Recreation (figure \@ref(fig:fig13))
+- Scientific research (figure \@ref(fig:fig16))
 

### 2022-04-23 outputs/paper/paper.Rmd
Introduction writing (1)

@@
 # Introduction
-First paragraph : broader context for motivation
+Although we are currently heading back to life before COVID-19, it is no exaggeration to say that COVID-19 has altered substantial portions of life style especially until end of 2021.
+For instance, remote work or wearing masks in public spaces has become usual.
+Of course, many of us feel uncomfortable about the strict sanctions.
+Then, my question was who should be in charge of this pandemic.
+Speaking of results, it should be all of us.
+Probably, without radical advances in technology, such virus would not exist.
+However, blaming each of us for the pandemic is very rare, rather many of us tend to blame government for lack of professional actions.
+Then, which fields  are more vulnerable to criticism?
+This brings me to write this paper.
 
-Second paragraph : some detail about what the paper is about
+This paper is going to explore changes in U.S citizen opinions on government spending levels before and after COVID-19.
+Following that, I have obtained U.S GSS 2018 and 2021, and sorted variables that I considered as potential variables changed during the pandemic.
+Since I aimed to figure out government spending on various fields, I mainly extracted national spending levels as the variables.
+However, there remains a clear gap that needs to be filled.
+Because this paper is about general thoughts changes on government spending levels, it was hard to make decisions that some changes were due to the pandemic or not.
+For instance, 26% of participants said national spending on arms was too much in 2018, and 32% of them said it was too much in 2021.
+It is hard to tell whether the increase is solely due to the pandemic or not.
 
-Third paragraph: a clear gap that needs to be filled
+In order to discern the changes by the pandemic, I was required to research U.S society backgrounds in 2018 and 2021, and they were used to along with data analysis.
+By plotting graphs for comparison, I sorted responses as three factors: Positive, Negative and unchanged.
+For instance, for positive response, many of participants required more national budgets on welfare.
+In general, national spending on public service such as education earned positive.
+On the other hand, national spending on arms, or foreign aids earned negative.
+Of course, there exists exceptions, and they are going to be dealt with in result and discussion session.
 
-Fourth: what was done, what was found
+This paper is important in a sense that it can present new plans and visions for government budgets. Also, in a broader sense, other countries can refer to this paper for simple comparison. 
+Before we jump into the main session, I am going to briefly introduce you remained index of this paper, and what they are about.
 
-5: why it is important
+2) Data: you are going to see how data was collected and sorted
+
+3) Model: you are going to observe which variables belong to negative, positive and unchanged.
+
+4) Results: you are going to read summary and analysis of data.
+
+5) Discussion: what is remained to be solved.
+
+6) Appendix and References.
 
@@
 
-First, to make the demarcation between data session and appendix, I focused on two parts: whether there existed different patterns or noticeable changes between two graphs 2018 and 2021.
+First, to make the demarcation between data session and appendix, I focused on two parts: whether there existed different patterns and noticeable changes between two graphs 2018 and 2021.
 For instance, figure \@ref(fig:fig7) shows us same pattern between 2018 and 2022, and there exists subtle changes.
@@
 For an another example, figure \@ref(fig:fig2) presents different pattern between 2018 and 2021.
-Therefore, with respect to two the aspects, I am going to explain my data here.
+Therefore, with respect to the two aspects, I am going to explain my data here.
 

### 2022-04-23 outputs/paper/paper.Rmd
Model coding (1)

@@
 c_data <- read_csv("outputs/combined_data.csv")
+reduced_data1 <- read_csv("outputs/reduced1_data.csv")
+reduced_data2 <- read_csv("outputs/reduced2_data.csv")
+
 ```
@@
 Following that, I obtained datasets from U.S GSS 2018 and 2021 considering first outbreak of COVID-19, which was in Dec 2019.
+Dataset collected through US GSS is aimed for the goal that enabling the cleanest comparison to show changes in public opinion in the United States.
+Usually, it is conducted in person, however because of pandemic, this time it was conducted via online.
 There are numerous surveys about COVID-19, however in order to observe general thought changes, they are not as appropriate as U.S GSS.
@@
 These numbers might seem subtle, however if we put this into whole population of U.S, it is 25.7 million and 30.34 million respectively.
+According to Forbes research, foreign aid spent by U.S is decreasing over years which was 46 billion dollars in 2018 and 38 billion dollars in 2021.
+In other words, this contradiction means that there could be another factors that possibly influenced thoughts on foreign aids.
 
@@
 Most of participants were in good health conditions in figure \@ref(fig:fig18). One thing to notice here is that participants health conditions increased.
+
+# Model
+
+Since I do not have exact y-value in my data, I am going to create representative from three categories: positive, negative and unchanged, then double check whether they belong to appropriate groups or not.
+To do that, I am going to create a multiple linear regression model.
+Since changes must move together once they belong to same groups, I decided that multiple linear regression model can explain better than others.
+In order to sort variables into the three groups, I followed the result from data session, and set changes less than 5% as unchanged.
+The outcome is as followed:
+
+1) Positive: Drug Addicts, Welfare,
+
+2) Negative: Foreign Aid, Arms, Big Cities problem, Health, Race
+
+3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security.
+
+natheal, natsci, natroad, natenrgy and natcrime appeared in the models insignificant
+
+```{r, include = FALSE}
+d_data <- rbind(reduced_data1, reduced_data2)
+model1 <- lm(natfare ~ natdrug, data = d_data)
+model2 <- lm(nataid ~ natarms + natcity + natheal + natrace, data = d_data )
+model3 <- lm(natchld ~ natcrime + nateduc + natenrgy + natenvir + natmass + natpark + natroad + natsci + natsoc, data = d_data)
+```
+
+\newpage
+
+# Results
 
@@
 
-\newpage
-
-# Results
-According to Forbes research, foreign aid spent by U.S is decreasing over years which was 46 billion dollars in 2018 and 38 billion dollars in 2021.
-In other words, this contradiction means that there could be another factors that possibly influenced thoughts on foreign aids.
-
 # Discussion
@@
 Thank you for participating in our survey. If you have any questions please do not hesitate to contact us.
-sangwoong.lee@maill.utoronto.ca and young.suk@mail.utoronto.ca
+sangwoong.lee@maill.utoronto.ca
 

### 2022-04-23 scripts/data-preparation.R

@@ -201,4 +201,5 @@ c_data <-
 write_csv(c_data, 'outputs/combined_data.csv')
 
 
+
          

### 2022-04-23 outputs/paper/paper.Rmd
Result session writing started

@@
 
-1) Positive: Drug Addicts, Welfare,
+1) Positive: Drug Addicts, Welfare
 
@@
 
-3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security.
+3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security
 
-natheal, natsci, natroad, natenrgy and natcrime appeared in the models insignificant
+4) Government responsibility : helppoor, helpsick, eqwlth
+
+natheal, natsci, natroad, natenrgy and natcrime appeared in the corresponding models insignificant.
+However, this does not mean that I needed to re-arrange the groups, rather it shows that there is no linear relations with chosen y- value.
+Also, since different changes in percentage is evident, they must belong to original groups, and further interpretation is going to be made in result and discussion session.
 
@@
 model1 <- lm(natfare ~ natdrug, data = d_data)
-model2 <- lm(nataid ~ natarms + natcity + natheal + natrace, data = d_data )
+model2 <- lm(nataid ~ natarms + natcity  + natrace + natheal, data = d_data )
 model3 <- lm(natchld ~ natcrime + nateduc + natenrgy + natenvir + natmass + natpark + natroad + natsci + natsoc, data = d_data)
+model4 <- lm(helppoor ~  helpsick + eqwlth, data = d_data)
 ```
 
-\newpage
+# Results
 
-# Results
+In this session, I am going to summarize results from model and data session.
+
+First, let's take a look at the positive group.
+This also includes government responsibility group excluding helppoor as they both present voices on more government actions needed.
+Following that, figure \@ref(fig:fig6), figure \@ref(fig:fig10), figure \@ref(fig:fig20), and figure \@ref(fig:fig21) belong to this group.
+One interesting result is national spending levels on drug figure \@ref(fig:fig6).
+According to CDC, death from overdoes in U.S is increasing over years, but the fact that respondents moved to "About right" on the national spending level contradicts with the CDC data, although majority of them answered "Too little", 70% in 2018 and 61% in 2021.
+Unlike small increase in drug overdoes death in other years, it noticeably increased during the pandemic.
+The movement conveys an important message here: indifference.
+During the pandemic, especially between 2020 and 2021, there was strict lock down policy in U.S.
+Other than essential workers, most had to stay at home, which caused for people to be indifferent about their surroundings.
+In addition to the indifference from the lock down, it also brought financial problems.
+People who could work remote was rare comparing to people who could not.
+In other words, there was serious layoffs although government gave financial aids.
+This naturally caused many to consider more actions and funds were needed, which appeared in welfare (figure \@ref(fig:fig10)), helppoor (figure \@ref(fig:fig20)) and eqwlth (figure \@ref(fig:fig21)).
+
+Second, let's explore into the negative group: Figure \@ref(fig:fig1), Figure \@ref(fig:fig2), Figure \@ref(fig:fig4), Figure \@ref(fig:fig11), and Figure \@ref(fig:fig14).
+They all show increase in "Too much".
+There were few things that were showed very interesting results.
+One was health part.
+It is true that majority answered "Too little" for national spending on healthcare in both years.
+However, it dropped by 5.8%.
+Although this is little above from the standard of change I set in the model session, and it did not solely fit into the group, considering 2020 survey was conducted during the pandemic, it was surprising.
+According to Forbes, critical care beds per capita in U.S is the highest In other words, unlike other countries, U.S was comparatively able to handle serious patients well.
+Also, as the pandemic went on, the virus got weaker, which enabled people to treat themselves at home.
+I suspect that this is why there was drop in "Too little".
+Therefore, health must stay in the negative group.
+In addition to the health part, race presented very interesting result as well.
+Black Lives Matter was a big issue during 2020,however, voice for more actions dropped over the years.
+It is absolutely true that there should not be any discrimination against races.
+However, violence cannot be justified under the name of equality.
+After George Floyd was murdered by a police officer in May 25, 2020, serious riots and looting occurred all over U.S.
+I think the drop in "Too little" was appeared as a counteraction of the violence.
+The rest variables make sense if you think of the pandemic situation.
+During the pandemic, not only vaccines were more needed than guns, but taking care of own nation came first than helping other countries.
+Therefore, it is natural to observe the negative in arms, foreign aids and big city problems.
+
+Last is the unchanged group:  Figure \@ref(fig:fig3), Figure \@ref(fig:fig5), Figure \@ref(fig:fig7), Figure \@ref(fig:fig8), Figure \@ref(fig:fig9), Figure \@ref(fig:fig12), Figure \@ref(fig:fig13), Figure \@ref(fig:fig15), Figure \@ref(fig:fig16) and Figure \@ref(fig:fig17).
+This group can be interpreted as a group that is absolutely essential in society. For instance, no matter what we face, education 
+1. Essential
+2. Indifference regarding the virus.
+
+# Discussion
+
+## Summary
+
+## Weaknesses and how we should proceed in the future
 
@@
 
-# Discussion
-
-## Summary
-
-## Weaknesses and how we should proceed in the future
-
 \newpage
@@
 U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.
+https://www.forbes.com/sites/niallmccarthy/2020/03/12/the-countries-with-the-most-critical-care-beds-per-capita-infographic/?sh=347315dc7f86

### 2022-04-23 outputs/paper/paper.Rmd
result session writing done

@@
 
+3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security
 Last is the unchanged group:  Figure \@ref(fig:fig3), Figure \@ref(fig:fig5), Figure \@ref(fig:fig7), Figure \@ref(fig:fig8), Figure \@ref(fig:fig9), Figure \@ref(fig:fig12), Figure \@ref(fig:fig13), Figure \@ref(fig:fig15), Figure \@ref(fig:fig16) and Figure \@ref(fig:fig17).
-This group can be interpreted as a group that is absolutely essential in society. For instance, no matter what we face, education 
-1. Essential
-2. Indifference regarding the virus.
+This group can be interpreted as a group that is absolutely essential in society regardless the virus.
+For instance, no matter what we face, education must go on.
+In a same sense, other variables must go on regardless the virus.
+One thing to notice here is the outdoor services such as mass transportation, park or roads.
+One of major changes before and after the pandemic is virtual life.
+Many facilities ran virtually, so I assumed that national spending on outdoor services would belong to the negative group.
+However, it turned out to be unchanged.
+This means that they jumped clear of the pandemic.
 
@@
 ## Summary
+
+## what is something that we learn about the world?
 

### 2022-04-24 outputs/paper/paper.Rmd
grammer edited (1)

--- 2022-04-23 outputs/paper/paper.Rmd
@@
 # Introduction
-Although we are currently heading back to life before COVID-19, it is no exaggeration to say that COVID-19 has altered substantial portions of life style especially until end of 2021.
+Although we are currently heading back to the life before COVID-19, it is no exaggeration to say that COVID-19 has altered substantial portions of life style.
 For instance, remote work or wearing masks in public spaces has become usual.
@@
 Then, my question was who should be in charge of this pandemic.
-Speaking of results, it should be all of us.
+Speaking of the result, it should be all of us.
 Probably, without radical advances in technology, such virus would not exist.
-However, blaming each of us for the pandemic is very rare, rather many of us tend to blame government for lack of professional actions.
+However, situation of blaming each of us for the pandemic is very rare, rather many of us tend to blame government for lack of professional actions.
 Then, which fields are more vulnerable to criticism?
@@
 This paper is going to explore changes in U.S citizen opinions on government spending levels before and after COVID-19.
-Following that, I have obtained U.S GSS 2018 and 2021, and sorted variables that I considered as potential variables changed during the pandemic.
-Since I aimed to figure out government spending on various fields, I mainly extracted national spending levels as the variables.
+Following that, I have obtained data from U.S GSS 2018 and 2021, and sorted variables that I considered as potential variables that were possibly changed during the pandemic.
+I aimed to figure out government spending on various fields, so I mainly extracted national spending levels as the variables.
 However, there remains a clear gap that needs to be filled.
-Because this paper is about general thoughts changes on government spending levels, it was hard to make decisions that some changes were due to the pandemic or not.
+Because this paper is about general thought changes on government spending levels, it was hard to make clear decisions that the changes were due to solely the pandemic or not.
 For instance, 26% of participants said national spending on arms was too much in 2018, and 32% of them said it was too much in 2021.
-It is hard to tell whether the increase is solely due to the pandemic or not.
+It is hard to tell whether the increase was occurred solely from the pandemic or not.
 
-In order to discern the changes by the pandemic, I was required to research U.S society backgrounds in 2018 and 2021, and they were used to along with data analysis.
-By plotting graphs for comparison, I sorted responses as three factors: Positive, Negative and unchanged.
-For instance, for positive response, many of participants required more national budgets on welfare.
-In general, national spending on public service such as education earned positive.
-On the other hand, national spending on arms, or foreign aids earned negative.
-Of course, there exists exceptions, and they are going to be dealt with in result and discussion session.
+In order to discern the changes by the pandemic and others, I was required to research U.S society backgrounds from 2018 to 2021, and they were used along with data analysis.
+By plotting graphs for comparison between 2018 and 2021, I was able to sort the variables o=into three categories: Positive, Negative and unchanged reaction.
+For instance, for the positive reaction, there was drop in "Too much" and increase in "Too little" and vice versa for negative category.
+National spending on welfare and drug belong to the positive group.
+On the other hand, national spending on arms, or foreign aids belong to negative.
+Of course, there exists exceptions within the groups, and they are going to be dealt with in result and discussion session.
 
-This paper is important in a sense that it can present new plans and visions for government budgets. Also, in a broader sense, other countries can refer to this paper for simple comparison. 
+This paper is important in a sense that the pandemic is not over yet, so it can present new plans and visions for government budgets.
+Also, in a broader sense, other countries can refer to this paper for simple comparison.
 Before we jump into the main session, I am going to briefly introduce you remained index of this paper, and what they are about.
@@
 
-4) Results: you are going to read summary and analysis of data.
+4) Results: you are going to read summary and interpretation of data.
 
-5) Discussion: what is remained to be solved.
+5) Discussion: you are going to read reamined questions and weakness.
 
@@
 For this paper, I aimed to find out changes in U.S citizens' minds regarding the government before and after COVID-19 outbreak.
-Following that, I obtained datasets from U.S GSS 2018 and 2021 considering first outbreak of COVID-19, which was in Dec 2019.
+Following that, I obtained datasets from U.S GSS 2018 and 2021 considering the first outbreak of COVID-19, which was in Dec 2019.
 Dataset collected through US GSS is aimed for the goal that enabling the cleanest comparison to show changes in public opinion in the United States.
 Usually, it is conducted in person, however because of pandemic, this time it was conducted via online.
-There are numerous surveys about COVID-19, however in order to observe general thought changes, they are not as appropriate as U.S GSS.
-Most COVID-19 surveys were specifically aimed for healthcare fields.
+There are numerous surveys regarding COVID-19, however in order to observe general thought changes, they are not as appropriate as U.S GSS since most COVID-19 surveys were specifically aimed for healthcare fields.
 For instance, whether healthcare system was enough to cover all patients or not was a major point for most COVID-19 surveys.
-On the other hand, U.S GSS datasets included more various fields such as national spending on drug, crime and etc, thus it can rather represent more general changes than specific areas.
+On the other hand, U.S GSS datasets included more various fields such as national spending on drug, crime and etc, thus it enabled to represent more general changes.
 Among countless variables existing in U.S GSS, I chose national spending levels and government actions.
@@
 
-First, to make the demarcation between data session and appendix, I focused on two parts: whether there existed different patterns and noticeable changes between two graphs 2018 and 2021.
+First, to make the demarcation between data session and appendix, I focused on two parts: whether there existed different patterns or noticeable changes between two graphs 2018 and 2021.
 For instance, figure \@ref(fig:fig7) shows us same pattern between 2018 and 2022, and there exists subtle changes.
-On the other hand, although figure \@ref(fig:fig6) presents the same pattern, changes in percentage are relatively fluctuating than others.
+On the other hand, although figure \@ref(fig:fig6) presents the same pattern, but changes in percentage are relatively fluctuating than others.
 For an another example, figure \@ref(fig:fig2) presents different pattern between 2018 and 2021.
@@
 This two variables are very similar.
-Income equality is regarding whether government should impose more taxes on the rich for better income equality or not, and help poor is whether government should be responsible for helping the poor or not.
-Thankfully, they both present similar pattern, which enhances the reliability about the survey.
-Majority thinks that government and individuals both are responsible for income differences.
-One thing to notice here is that voice for government responsibility increased over years.
+Income equality was regarding whether government should impose more taxes on the rich for better income equality or not, and help poor was whether government should be responsible for helping the poor or not.
+Thankfully, they both presented similar pattern, which enhanced the reliability about the survey.
+Majority thought that government and individuals both were responsible for income differences.
+One thing to notice here was that voice for government responsibility increased over years.
 
@@
 In 2020 - 2021 when U.S GSS 2021 was conducted, although COVID-19 cases did not surge up as much as 2022, but with eyes in 2021, it was increasing.
-However, before and after COVID-19, there is no difference in response regarding government actions toward the sick.
-Majority think that more actions needed toward the sick from the government
+However, there was no difference in response regarding government actions toward the sick.
+Majority thought that more actions needed toward the sick from the government
 
@@
 
-Since I do not have exact y-value in my data, I am going to create representative from three categories: positive, negative and unchanged, then double check whether they belong to appropriate groups or not.
-To do that, I am going to create a multiple linear regression model.
-Since changes must move together once they belong to same groups, I decided that multiple linear regression model can explain better than others.
+Since I do not have exact y-value in my data, I am going to create representative from the three categories: positive, negative and unchanged, then double check whether they belong to appropriate groups or not.
+To do that, I am going to use multiple linear regression model.
+Since changes must move together once they belong to same groups, I decided that multiple linear regression model could explain better than others.
 In order to sort variables into the three groups, I followed the result from data session, and set changes less than 5% as unchanged.
@@
 
-1) Positive: Drug Addicts, Welfare
+1) Positive: Drug Addicts, Welfare, eqwlth, helppoor
 
@@
 
-3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security
+3) Unchanged: Childcare, Crime rates, Education, Energy, Environment, Mass Transportation, Park and recreation, Roads, Scientific research, Social security, helpsick
 
-4) Government responsibility : helppoor, helpsick, eqwlth
-
-natheal, natsci, natroad, natenrgy and natcrime appeared in the corresponding models insignificant.
-However, this does not mean that I needed to re-arrange the groups, rather it shows that there is no linear relations with chosen y- value.
-Also, since different changes in percentage is evident, they must belong to original groups, and further interpretation is going to be made in result and discussion session.
+natheal, natsci, natroad, and natpark appeared in the corresponding models insignificant.
+However, this does not mean that I needed to re-arrange the groups, rather it shows that there was no linear relations with chosen y- value.
+Also, since different changes in percentage is evident, they must belong to original groups, and further interpretation is going to be made regarding this in result and discussion session.
 
@@
 d_data <- rbind(reduced_data1, reduced_data2)
-model1 <- lm(natfare ~ natdrug, data = d_data)
+model1 <- lm(natfare ~ natdrug + eqwlth + helppoor , data = d_data)
 model2 <- lm(nataid ~ natarms + natcity  + natrace + natheal, data = d_data )
-model3 <- lm(natchld ~ natcrime + nateduc + natenrgy + natenvir + natmass + natpark + natroad + natsci + natsoc, data = d_data)
-model4 <- lm(helppoor ~  helpsick + eqwlth, data = d_data)
+model3 <- lm(helpsick ~ natchld + natcrime + nateduc + natenrgy + natenvir + natmass + natpark + natroad + natsci + natsoc, data = d_data)
+summary(model3)
 ```
@@
 First, let's take a look at the positive group.
-This also includes government responsibility group excluding helppoor as they both present voices on more government actions needed.
 Following that, figure \@ref(fig:fig6), figure \@ref(fig:fig10), figure \@ref(fig:fig20), and figure \@ref(fig:fig21) belong to this group.
-One interesting result is national spending levels on drug figure \@ref(fig:fig6).
+One interesting result is that national spending levels on drug figure \@ref(fig:fig6).
 According to CDC, death from overdoes in U.S is increasing over years, but the fact that respondents moved to "About right" on the national spending level contradicts with the CDC data, although majority of them answered "Too little", 70% in 2018 and 61% in 2021.
@@
 During the pandemic, especially between 2020 and 2021, there was strict lock down policy in U.S.
-Other than essential workers, most had to stay at home, which caused for people to be indifferent about their surroundings.
-In addition to the indifference from the lock down, it also brought financial problems.
+Other than essential workers, most had to stay at home, which I assumed to cause for people to be indifferent about their surroundings.
+In addition to the indifference from the lock down, the lock down also brought financial problems.
 People who could work remote was rare comparing to people who could not.
 In other words, there was serious layoffs although government gave financial aids.
-This naturally caused many to consider more actions and funds were needed, which appeared in welfare (figure \@ref(fig:fig10)), helppoor (figure \@ref(fig:fig20)) and eqwlth (figure \@ref(fig:fig21)).
+This naturally caused many to consider more actions and funds needed, which appeared in welfare (figure \@ref(fig:fig10)), helppoor (figure \@ref(fig:fig20)) and eqwlth (figure \@ref(fig:fig21)).
 
@@
 They all show increase in "Too much".
-There were few things that were showed very interesting results.
+There were few things that presented very interesting results.
 One was health part.
@@
 However, it dropped by 5.8%.
-Although this is little above from the standard of change I set in the model session, and it did not solely fit into the group, considering 2020 survey was conducted during the pandemic, it was surprising.
-According to Forbes, critical care beds per capita in U.S is the highest In other words, unlike other countries, U.S was comparatively able to handle serious patients well.
+Although this is little above from the standard of change I set in the model session, and the variable did not fit into the group, considering 2020 when the survey was conducted, it was surprising.
+According to Forbes, critical care beds per capita in U.S is the highest among many countries.
+In other words, unlike other countries, U.S was comparatively able to handle serious patients well.
 Also, as the pandemic went on, the virus got weaker, which enabled people to treat themselves at home.
@@
 In addition to the health part, race presented very interesting result as well.
-Black Lives Matter was a big issue during 2020,however, voice for more actions dropped over the years.
+Black Lives Matter was a big issue during 2020, however, voice for more actions dropped over the years.
 It is absolutely true that there should not be any discrimination against races.
@@
 After George Floyd was murdered by a police officer in May 25, 2020, serious riots and looting occurred all over U.S.
-I think the drop in "Too little" was appeared as a counteraction of the violence.
+I think the drop in "Too little" was occured as a counteraction of the violence.
 The rest variables make sense if you think of the pandemic situation.
@@
 Last is the unchanged group:  Figure \@ref(fig:fig3), Figure \@ref(fig:fig5), Figure \@ref(fig:fig7), Figure \@ref(fig:fig8), Figure \@ref(fig:fig9), Figure \@ref(fig:fig12), Figure \@ref(fig:fig13), Figure \@ref(fig:fig15), Figure \@ref(fig:fig16) and Figure \@ref(fig:fig17).
-This group can be interpreted as a group that is absolutely essential in society. For instance, no matter what we face, education 
-1. Essential
-2. Indifference regarding the virus.
+This group can be interpreted as a group that was absolutely essential in society regardless the virus.
+For instance, no matter what we face, education must go on.
+In a same sense, other variables must go on regardless the virus.
+One thing to notice here is the outdoor services such as mass transportation, park or roads.
+One of major changes before and after the pandemic is virtual life.
+Many facilities ran virtually, so I assumed that national spending on outdoor services would belong to the negative group.
+However, it turned out to be unchanged.
+This means that they jumped clear of the pandemic.
 
@@
 # Appendix {-}
-In this session, I am going to deal with remained data explanation. Since no dramatic changes were observed in remained variables, I combined them by patterns.
+In this session, I am going to deal with remained data explanation. Since no noticeable changes were observed in remained variables, I combined them by patterns.
 

### 2022-04-24 outputs/paper/paper.Rmd
Discussion writing (1)

@@
 After George Floyd was murdered by a police officer in May 25, 2020, serious riots and looting occurred all over U.S.
-I think the drop in "Too little" was occured as a counteraction of the violence.
+I think the drop in "Too little" was occurred as a counteraction of the violence.
 The rest variables make sense if you think of the pandemic situation.
@@
 # Discussion
+In this session, we are going to explore remained and unanswered questions from results session.
 
 ## Summary
+Throughout this paper, we have figured out U.S citizens' various responses regarding their government specifically between 2018 and 2021.
+By focusing on COVID-19 influences along with backgrounds, I have found out three responses: positive, negative and unchanged.
+For positive response, variables were collected with respect to changes moved to "Too little" or "About right" in national spending levels.
+I have observed that strict COVID-19 sanctions or ripple effects from the sanctions affected the thoughts on national spending levels on drug, Welfare and actions on equalizing income differences.
+Furthermore, the change in drug presented that potential indifference existing in U.S citizens minds.
+For negative response, variables were collected regarding changes moved to "Too much".
+I have figured out that the government successfuly dealt with the pandemic regarding healthcare, and nationalism took great deal of explanation for negative responses.
+Lastly, unchanged variables were mostly related to essential services such as road and education.
+Also, unexpectedly outdoor services dodged the ripple effects of the sanction.
 

### 2022-04-24 outputs/paper/paper.Rmd
Abstract and discussion session writing

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "First sentence. Second sentence. Third sentence. Last sentence."
+abstract: "This paper has been examined to find out U.S citizens' opinions on government budget sectors that were changed by COVID-19.
+I have found that there existed variables that presented negative, positive and unchanged responses.
+This is important in a sense that it relates to lives as well as becomes an indication for why such gap exited.
+We will discuss its importance in details later in discussion session."
 output:
@@
 Lastly, unchanged variables were mostly related to essential services such as road and education.
-Also, unexpectedly outdoor services dodged the ripple effects of the sanction.
+Also, unexpectedly outdoor services dodged the ripple effects from the sanction.
 
 ## what is something that we learn about the world?
+We have learned that there existed changes in U.S citizens' mind after COVID-19 breakout.
+However, considering the shock that COVID-19 gave us unlike other viruses such as Ebola, the change was subtle.
+In other words, the world keeps going by coping with such challenges.
 
-## Weaknesses and how we should proceed in the future
+## how we should proceed in the future
+As we are currently facing the end of pandemic, invisible problems will rise on the surface.
+Further surveys on various fields are needed to deal with them.
+For instance, racial problems will not sink unless we all try to solve them.
+Also, as my paper presented, essential fields like education or childcare must go on regardless the challenge because they are the future.
+
+## Weakness
+As US GSS aims to observe general thought changes, there existed limits on finding out sources of the change.
+For instance, figure \@ref(fig:fig14) clearly presented that there was negative responses regarding national spending levels on racial problems, however it was hard to tell whether it occured from COVID-19 or other factors such as BLM protest not.
 
@@
 --NORC ed.-- Chicago: NORC, 2019.
-https://www.forbes.com/sites/adamandrzejewski/2021/08/04/new-report-nearly-300-billion-in-foreign-aid-spent-by-us-government/?sh=6e3454774374
-https://www.cdc.gov/drugoverdose/deaths/index.html
+
+Andrzejewski, Adam.
+n.d.
+“New Report: Nearly $300 Billion in Foreign Aid Spent by U.S.
+Government.” Forbes.
+Accessed April 24, 2022.
+https://www.forbes.com/sites/adamandrzejewski/2021/08/04/new-report-nearly-300-billion-in-foreign-aid-spent-by-us-government/?sh=6e3454774374.
+
+Centers for Disease Control and Prevention. 2021. “Drug Overdose Deaths.” Www.cdc.gov. June 23, 2021. https://www.cdc.gov/drugoverdose/deaths/index.html.
 
 U.S. Census Bureau (2021). Population estimates. Retrieved from https://www.census.gov/quickfacts/fact/table/US/PST045221.
-https://www.forbes.com/sites/niallmccarthy/2020/03/12/the-countries-with-the-most-critical-care-beds-per-capita-infographic/?sh=347315dc7f86
+
+McCarthy, Niall.
+n.d.
+“The Countries with the Most Critical Care Beds per Capita [Infographic].” Forbes.
+Accessed April 24, 2022.
+https://www.forbes.com/sites/niallmccarthy/2020/03/12/the-countries-with-the-most-critical-care-beds-per-capita-infographic/?sh=347315dc7f86.
+‌

### 2022-04-24 outputs/paper/paper.Rmd
grammer edited overall

@@
 In order to discern the changes by the pandemic and others, I was required to research U.S society backgrounds from 2018 to 2021, and they were used along with data analysis.
-By plotting graphs for comparison between 2018 and 2021, I was able to sort the variables o=into three categories: Positive, Negative and unchanged reaction.
-For instance, for the positive reaction, there was drop in "Too much" and increase in "Too little" and vice versa for negative category.
+By plotting graphs for comparison between 2018 and 2021, I was able to sort the variables into three categories: Positive, Negative and unchanged reaction.
+For instance, for the positive reaction, there was drop in "Too much" and increase in "Too little" or "About right", and vice versa for negative category.
 National spending on welfare and drug belong to the positive group.
@@
 To do that, I am going to use multiple linear regression model.
-Since changes must move together once they belong to same groups, I decided that multiple linear regression model could explain better than others.
+Since direction of changes must move together once they belong to same groups, I decided that multiple linear regression model could explain better than others.
 In order to sort variables into the three groups, I followed the result from data session, and set changes less than 5% as unchanged.
@@
 In other words, the world keeps going by coping with such challenges.
+Also, many reported that their health condition is in good shape.
+figure \@ref(fig:fig18)
 
@@
 
-## End Page
-
-Thank you for participating in our survey. If you have any questions please do not hesitate to contact us.
-sangwoong.lee@maill.utoronto.ca
-
 \newpage

### 2022-04-27 scripts/data-preparation.R
Data preparation edited

@@ -199,6 +199,8 @@ c_data <-
 
 #### Save ####
 write_csv(c_data, 'outputs/combined_data.csv')
+write_csv(reduced_data1, 'outputs/reduced_data1.csv')
+write_csv(reduced_data2, 'outputs/reduced_data2.csv')
 
 
 

### 2022-04-27 scripts/data-preparation.R
Data preparation edited (2)

@@ -199,8 +199,8 @@ c_data <-
 
 #### Save ####
 write_csv(c_data, 'outputs/combined_data.csv')
-write_csv(reduced_data1, 'outputs/reduced_data1.csv')
-write_csv(reduced_data2, 'outputs/reduced_data2.csv')
+write_csv(reduced_data1, 'outputs/reduced1_data.csv')
+write_csv(reduced_data2, 'outputs/reduced2_data.csv')
 
 
 

### 2022-04-27 outputs/paper/paper.Rmd
Last updated, referenced updaterd

@@
 library(scales)
-library(modelsummary)
 ```

### 2022-04-27 outputs/paper/paper.Rmd
citation updated

@@
 
-This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr] was used to format this report.
+This report was created using `R` [@citeR] and its libraries `tidyverse` [@tidyverse], `dplyr` [@dplyr], were used to process and clean the data, and `ggplot` [@ggplot] `bookdown` [@bookdown] and `knitr` [@knitr], `scales` [@scales] was used to format this report.
 

### 2022-04-27 outputs/paper/paper.Rmd
github link updated

@@
 ---
-title: "Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
+title: "Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/COVID-19-Government]"
 subtitle: "COVID-19 influences on U.S citizens' mind regarding government actions"
